---
title: "linear model from Web"
author: "Chris Gonzalez"
date: "Summer 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
basicNN <- ggplot(data, aes(y = SIMS, x = ARM)) +
  geom_point() +
  labs(title = "SIMS ~ ARM") +
  theme(plot.title = element_text(hjust = 0.5))

basicNN
```

### Numerical results
```{r}
cor(SIMS~ARM,data=data)
```
Based on the provided numerical data, where the mean is approximately 0.6860073, it indicates a moderate relationship between the two variables.

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

Considering the provided information, with a residual standard error of 1.226 and an adjusted R-squared of 0.0467, the analysis suggests that the model may not be the most suitable for making accurate predictions. The low value of the adjusted R-squared indicates that only a small proportion of the variability in the response variable can be explained by the predictor variables. Additionally, the relatively high residual standard error indicates that there is significant unexplained variability in the model

#### Predict at target point

```{r}
mydata<- data.frame (GRIP=88, ARM= 104)
```



#### scatterplot with model fit
  

## Model 2 SIM~GRIP

### Now add in scatterplot


### Numerical results 


### Inferential  (Build model.2)
  

#### predict model.2 at target point

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

