---
title: "linear model from Web"
author: "Chris Gonzalez"
date: "Summer 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
basicNN <- ggplot(data, aes(y = SIMS, x = ARM)) +
  geom_point() +
  labs(title = "SIMS ~ ARM") +
  theme(plot.title = element_text(hjust = 0.5))

basicNN
```

### Numerical results
```{r}
cor(SIMS~ARM,data=data)
```
Based on the provided numerical data, where the mean is approximately 0.6860073, it indicates a moderate relationship between the two variables.

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

Considering the provided information, with a residual standard error of 1.226 and an adjusted R-squared of 0.0467, the analysis suggests that the model may not be the most suitable for making accurate predictions. The low value of the adjusted R-squared indicates that only a small proportion of the variability in the response variable can be explained by the predictor variables. Additionally, the relatively high residual standard error indicates that there is significant unexplained variability in the model

#### Predict at target point

```{r}
mydata<- data.frame (GRIP=88, ARM= 104)
predict.lm(model.1,mydata, interval = "prediction")
```
Based on the provided information, the predicted value is 1.58, and the prediction interval is given as (-0.86, 4.02). Since the predicted value of 1.58 falls within the lower end of the prediction interval, it suggests that the actual value is more likely to be closer to the lower end of the range (-0.86) rather than the upper end (4.02). However, without additional information or context, it is challenging to determine the exact position within the prediction interval.


#### scatterplot with model fit
```{r}
basicNN <- ggplot(data, aes(y = SIMS, x = ARM)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "SIMS ~ ARM") +
  theme(plot.title = element_text(hjust = 0.5))

basicNN

```

## Model 2 SIM~GRIP


### Now add in scatterplot
```{r}
mygrip <- ggplot(data, aes(y = SIMS, x = GRIP)) +
  geom_point() +
  labs(title = "SIMS ~ GRIP") +
  theme(plot.title = element_text(hjust = 0.5))

mygrip
```

### Numerical results 
```{r}
cor(SIMS~GRIP,data=data)
```
Based on the provided numerical results, the correlation coefficient between SIMS and ARM is 0.6860073, which is higher than the correlation coefficient between SIMS and GrIP, which is 0.6398458. This indicates that there is a stronger linear relationship between SIMS and ARM compared to SIMS and Grip. The higher correlation value suggests that changes in ARM are more closely associated with changes in SIMS than changes in Grip.



### Inferential  (Build model.2)
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```
Based on the provided information, where the residual standard error for the analysis using SIMS and ARM is 1.295 and the adjusted R-squared is 0.4053, it suggests that the model using SIMS and ARM as predictors provides a better fit to the data compared to the model using SIMS and GRIP.The lower residual standard error of 1.295 indicates that the model using SIMS and ARM has less unexplained variability compared to the model using SIMS and GRIP. Additionally, the higher adjusted R-squared value of 0.4053 suggests that a larger proportion of the variability in the response variable can be explained by the predictors in the model using SIMS and ARM.
Therefore, based on these metrics, analyzing the data using SIMS and ARM is considered a better approach.

#### predict model.2 at target point

```{r}
predict.lm(model.2,mydata, interval = "prediction")
```
The given regression analysis yields a predicted value of -0.8089323 for the response variable. The corresponding prediction interval suggests that the actual response value is likely to fall within the range of -3.38434 to 1.766475. This interval captures the uncertainty associated with the prediction and provides a range of plausible values for the response variable. Therefore, based on the analysis, the predicted value falls within the lower end of the prediction interval, indicating a higher likelihood of the actual value being closer to the lower bound (-3.38434) rather than the upper bound (1.766475).

#### now add the model fit to our plot for model.2
  
```{r}
mygrip <- ggplot(data, aes(y = SIMS, x = GRIP)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "SIMS ~ GRIP") +
  theme(plot.title = element_text(hjust = 0.5))

mygrip

```

## Model 3 SIM~ARM+GRIP


### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```
With the additional information provided, which indicates a correlation coefficient of 0.7326545 between ARM and GRIP, it suggests a strong positive linear relationship between these two variables.A correlation coefficient of 0.7326545 indicates a fairly high correlation, implying that there is a significant tendency for the values of ARM and GRIP to move together in a linear fashion. As the correlation coefficient approaches 1, it indicates a stronger positive linear relationship between the variables.
  
### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

Based on the additional information provided, where the residual standard error for the model using ARM and GRIP is 1.144 and the adjusted R-squared is 0.5358, it suggests that the model has a relatively low residual standard error and a moderate adjusted R-squared value.The lower residual standard error of 1.144 indicates that the model has less unexplained variability, which implies that the model is better at predicting the response variable (SIMS) based on the predictors (ARM and GRIP).The adjusted R-squared value of 0.5358 suggests that approximately 53.58% of the variability in the response variable can be explained by the predictors in the model using ARM and GRIP. This indicates that the model provides a reasonable fit to the data and that ARM and GRIP are informative in explaining the variation in SIMS.


#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

